On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-06-30 documents/paper.tex
Modelling distribution

\null\begin{tabular}[t]{l@{}}
  {Daniel Correia}\ \orcidlink{0000-0002-9353-0216}  \\
  \textit{York University}
\end{tabular}

@@

	Additionally, other sterilization techniques may produce superior results and should be evaluated in the same context. Data on far UV [Buonanno 2017] indicate safety.\\

@@

\begin{multicols}{1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The chain of literature Fruluch -> ([Sun ] | [Yang 2015]) establishes that spherical virions possess a weak dipole resonance mode which happens to fall within the microwave spectrum, at approximately the X-band (6-10 GHz).

This is a non-ionizing, non-thermal technique;

\paragraph{\textbf{Time dependence}}\

@@

\footnote{All values have been converted to $W/m^2$ to avoid confusion.}

@@

A bronchoscopic technique may therefore be effective, very similarly to that demonstrated by [Yuan 2019]: the bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 7 mm thick [Chekan 2016].

There is considerable tolerance in the

Further study is required to validate this method.

@@

\paragraph{Biasing}\

In our simulations, the varactor-tuned feedback circuit appeared to be particularly sensitive to the introduction of bias-tees.

The gate must be weakly pulled to ground, otherwise stray charge destroys the oscillation.

\fancyhead[C]{style 1 with thin line}

With 0.79 mm FR4 substrate and 0.2 mm (8 mil) wide traces, the maximum impedance achievable was about 115 ohms, which did not appear to be sufficient as an RF choke. Use of defected grounds can increase inductance, but this was not evaluated.

If suitably high-impedance traces are not available, a common technique is to use a quarter-wavelength line (approximately 6 mm long with the above parameters at 8 GHz) terminated with a stub to produce a virtual short or open circuit [Seo 2007].

However, reflections from these structures still appeared to distort the frequency/phase response beyond repair, even with ostensibly wideband stubs [Syrett 1980].

\noindent\fbox{\parbox{\linewidth}{
	Rebuke: despite this blather, many other papers have had success with bias-tees at these frequencies.
}}

Alternate methods evaluated, failures:

In production, these could be accomodated by graphite-polymer printed resistors.

Odd-pole varactor-loaded combline filters appeared to have excellent phase and frequency response; however, the geometry necessitates low-inductance via stitching to the ground plane.

%\noindent\fbox{\parbox{\linewidth}{
\begin{autem}
	{\it autem} Others have had great success with varactor-tuned comblines, especially non-grounded lines.
\end{autem}

[Tsuru 2008 fig. 10] is an excellent review of various oscillator designs.

The parasitic inductance of common varactors appears to become problematic at these frequencies (but not for non-wideband use).

\paragraph{\textbf{Spacing}}\

FDTD results still yielded some coupling at 2 mm isolation.

\paragraph{\textbf{Via stitching}}\

Rather than the almost universal technique of via stitching components immediately to the ground plane (a tedious process with our prototyping setup), a large ground pour on the component layer was used wherever ground was needed, as mentioned in [Hunter? combline]. Since we use microstrip rather than coplanar waveguide,

Since the ground plane does not participate in the DC bias at all, no vias are required in the final device. This means that the drilling, electroless strike and electroplating steps are unnecessary for production.

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Acknowledgements}\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This paper is not novel enough to deserve this chapter, but those to be acknowledged are.

The authors of the original papers deserve the credit for this entire work;  it is rare that such a monumental finding is served on a silver platter.

Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.

Dr. Dainis' videos on microbiological technique were also useful.

Thanks to the professors at York and beyond for returning my emails.

Thanks to L.H. for wisdom regarding this project.

Thanks to P.B and H.P. for tolerating ramblings and M. for the hug.

Special thanks to all the people - most equally capable of writing this paper if provided the opportunity - who work menial shifts at the component suppliers that remained open that were so critical. Hopfstader be damned; despite the name below the abstract, this paper is of course entirely the result of circumstance and luck.

Chiefly among the enablers are of course my parents, Doris and Brian, without whom this work would have been done by someone else, and who also supported this work financially.

One Very Important Thought

>>>>

\null\begin{tabular}[t]{l@{}}
  {Daniel Correia}\ \orcidlink{0000-0002-9353-0216}  \\
  \textit{????????? York??????}
\end{tabular}

@@

	Additionally, other sterilization techniques may produce superior results with less faffing about and should be evaluated in the same context. Data on far UV [Buonanno 2017] indicates safety.\\

@@

\clearpage
\begin{multicols}{1}

\paragraph{{\Large the gist}}\

Any claims of

The chain of literature 
%
[Fr\"{o}hlich 1968] \textrightarrow \ [Fr\"{o}hlich 1980] \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have probably missed several steps in this chain out of haste.} apparently culminates in the flagship work we focus on in this paper,

{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
%

estabilishes that - unique to certain viruses, and apparently unlike human cell structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-band (6-10 GHz).

More critically, [Yang 2015] (in parallel with [Hung 2014]) theoretically model and then experimentally demonstrate that the electric field strength required to produce an amplitude of vibration sufficient to tear the lipid envelope of the order of magnitude of 100 V/m.

They demonstrate this with both a plaque and PCR assay, with fantastic agreement to the theoretical model.

This is a non-ionizing, non-thermal technique.

Microwave resonant absorption of viruses through dipolar coupling with confined acoustic vibrations

\footnote{This {\it confined} acoustic resonance is apparently distinct from common-and-garden pipe-organ acoustic resonance. Rather than simple covalent or Lennard-Jones interaction between particles, if [Fr\"{o}hlich 1968] is to be believed at these nanoscopic scales a sort of coherent wavefunction is set up among the particles of the virus which produces coupling modes not otherwise expected. We confess to not yet understanding this phenomenon; fortunately, while helpful, the details of how this mode appears is not critical to implementing this technique.}

\footnote{``{For example, below about 6 GHz, where EMFs penetrate deep into tissue (and thus require depth to be considered), it is useful to describe this in terms of “specific energy absorption rate” (SAR), which is the power absorbed per unit mass $(W/kg)$. Conversely, above 6 GHz, where EMFs are absorbed more superficially (making depth less relevant), it is useful to describe exposure in terms of the density of absorbed power over area $W/m^2$, which we refer to as “absorbed power density”}'' [ICNIRP 2020 \faExternalLink] }

@@

\clearpage
\paragraph{\textbf{Time dependence}}\

@@

\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 50 \text{mW/cm}^2$}

@@

A bronchoscopic technique may therefore be effective, very similarly to that demonstrated by [Yuan 2019]: in adults, the bronchi are less than 2 mm thick [Theriault 2018] and the lungs themselves are only on the order of 7 mm thick [Chekan 2016].

The main bronchus is about 8 mm in diameter, which is smaller than the patch antenna used here; a monopole (or multiple, phased monopoles) like is probably more suitable.

@@

@@

\subfile{acknowledgement}
